TreeFelling_Draft

### 2021-11-08 R/DESIGNATION_DRAFT.Rmd
After doc review

if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")) {
  # Hollow trees = fuelwood:
  inventoryH <- inventoryG %>%
    mutate(DeathCause = ifelse(ProbedHollow == "1", "hollowfuel", NA)) # remplacer NA par DeathCause dans le simulateur ONF

>>>>

if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")) {
  # Hollow trees = fuel wood:
  inventoryH <- inventoryG %>%
    mutate(DeathCause = ifelse(ProbedHollow == "1", "hollowfuel", NA)) # remplacer NA par DeathCause dans le simulateur ONF

### 2021-11-08 R/TreeFelling_Draft.Rmd
loggingsimulation function and doc refresh
After doc review

inventory
multilignes "MainTrail ", "2ndTrail"
vecteur "AccessibleTreesPoints", "SelectedTreesPoints",  "AvenirTreesPoints",  "ReserveTreesPoints", "DeadTreesPoints", "HollowTreesPoints" et "FuelwoodTreesPoints"

@@

inventory <- addtreedim(inventorycheckformat(Paracou6_2016))

>>>>

inventory
multilignes "MainTrail ", "2ndTrail"
vecteur "AccessibleTreesPoints", "SelectedTreesPoints",  "AvenirTreesPoints",  "ReserveTreesPoints", "DeadTreesPoints", "HollowTreesPoints" et "Fuel woodTreesPoints"

@@

inventory <- addtreedim(inventorycheckformat(Paracou6_2016), volumeparameters = ForestZoneVolumeParametersTable)
